Blocking-resistant communication\\through domain fronting

### 2014-07-16 docs/meek.tex
Typo.
Make the ciphersuite figure take the whole width.
Might cut this figure.
Psiphon.

% Lantern
% Psiphon
% Infranet
% Freegate
% Ultrasurf
% Dust

@@

\begin{figure}

\begin{subfigure}[t]{0.30\textwidth}
\begin{minipage}[t][17ex][t]{0.30\textwidth}
\tiny
\begin{verbatim}
TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_RSA_WITH_RC4_128_SHA
TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
TLS_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
TLS_RSA_WITH_3DES_EDE_CBC_SHA
\end{verbatim}
\end{minipage}
\caption{meek-client}
\label{fig:ciphersuites:meek-client}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\begin{minipage}[t][48ex][t]{0.30\textwidth}
\tiny
\begin{verbatim}
TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
TLS_ECDHE_RSA_WITH_RC4_128_SHA
TLS_DHE_RSA_WITH_AES_128_CBC_SHA
TLS_DHE_DSS_WITH_AES_128_CBC_SHA
TLS_DHE_RSA_WITH_CAMELLIA_128_CBC_SHA
TLS_DHE_DSS_WITH_CAMELLIA_128_CBC_SHA
TLS_DHE_RSA_WITH_AES_256_CBC_SHA
TLS_DHE_DSS_WITH_AES_256_CBC_SHA
TLS_DHE_RSA_WITH_CAMELLIA_256_CBC_SHA
TLS_DHE_DSS_WITH_CAMELLIA_256_CBC_SHA
TLS_DHE_RSA_WITH_3DES_EDE_CBC_SHA
TLS_DHE_DSS_WITH_3DES_EDE_CBC_SHA
TLS_ECDH_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDH_RSA_WITH_AES_128_CBC_SHA
TLS_ECDH_ECDSA_WITH_AES_256_CBC_SHA
TLS_ECDH_RSA_WITH_AES_256_CBC_SHA
TLS_ECDH_ECDSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDH_RSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDH_ECDSA_WITH_RC4_128_SHA
TLS_ECDH_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_CAMELLIA_128_CBC_SHA
TLS_RSA_WITH_AES_256_CBC_SHA
TLS_RSA_WITH_CAMELLIA_256_CBC_SHA
TLS_RSA_WITH_SEED_CBC_SHA
SSL_RSA_FIPS_WITH_3DES_EDE_CBC_SHA
TLS_RSA_WITH_3DES_EDE_CBC_SHA
TLS_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_RC4_128_MD5
\end{verbatim}
\end{minipage}
\caption{Firefox 24}
\label{fig:ciphersuites:firefox}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\begin{minipage}[t][27ex][t]{0.30\textwidth}
\tiny
\begin{verbatim}
TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
TLS_DHE_RSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_ECDSA_WITH_CHACHA20_POLY1305_SHA256
TLS_ECDHE_RSA_WITH_CHACHA20_POLY1305_SHA256
TLS_RSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
TLS_DHE_RSA_WITH_AES_256_CBC_SHA
TLS_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_RC4_128_SHA
TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
TLS_DHE_RSA_WITH_AES_128_CBC_SHA
TLS_DHE_DSS_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_RC4_128_MD5
TLS_RSA_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_3DES_EDE_CBC_SHA
\end{verbatim}
\end{minipage}
\caption{Chrome 33}
\label{fig:ciphersuites:chrome}
\end{subfigure}

\caption{Differences in ciphersuites offered by
our \meekclient\ program when it accesses the network directly,
and by two web browsers.
The distinctive ciphersuites offered by \meekclient\ can be used as part of a blocking fingerprint.
As a remedy we have \meekclient\ proxy its TLS through a web browser extension.
}
\label{fig:ciphersuites}
\end{figure}

@@

To explain the phenomenon, recall that we use browsers to handle HTTPS connections for meek in order
to hide TLS handshake characteristics.
Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
records meek's traffic.
In contract, normal users may not have persistent connections to Google. For example, a user may search a keyword on
Google, click a result, and then close the tab that displays search results. The browser may close the 
connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
opens a new connection. In this case, small requests do not have such opportunity for batching.

>>>>

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
Psiphon uses domain fronting based on meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.

% Lantern
% Infranet
% Freegate
% Ultrasurf
% Dust

@@

\begin{figure*}
\centering
\begin{subfigure}[t]{0.30\textwidth}
\begin{minipage}[t][17ex][t]{0.30\textwidth}
\tiny
\begin{verbatim}
TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_RSA_WITH_RC4_128_SHA
TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
TLS_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
TLS_RSA_WITH_3DES_EDE_CBC_SHA
\end{verbatim}
\end{minipage}
\caption{meek-client}
\label{fig:ciphersuites:meek-client}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\begin{minipage}[t][48ex][t]{0.30\textwidth}
\tiny
\begin{verbatim}
TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
TLS_ECDHE_RSA_WITH_RC4_128_SHA
TLS_DHE_RSA_WITH_AES_128_CBC_SHA
TLS_DHE_DSS_WITH_AES_128_CBC_SHA
TLS_DHE_RSA_WITH_CAMELLIA_128_CBC_SHA
TLS_DHE_DSS_WITH_CAMELLIA_128_CBC_SHA
TLS_DHE_RSA_WITH_AES_256_CBC_SHA
TLS_DHE_DSS_WITH_AES_256_CBC_SHA
TLS_DHE_RSA_WITH_CAMELLIA_256_CBC_SHA
TLS_DHE_DSS_WITH_CAMELLIA_256_CBC_SHA
TLS_DHE_RSA_WITH_3DES_EDE_CBC_SHA
TLS_DHE_DSS_WITH_3DES_EDE_CBC_SHA
TLS_ECDH_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDH_RSA_WITH_AES_128_CBC_SHA
TLS_ECDH_ECDSA_WITH_AES_256_CBC_SHA
TLS_ECDH_RSA_WITH_AES_256_CBC_SHA
TLS_ECDH_ECDSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDH_RSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDH_ECDSA_WITH_RC4_128_SHA
TLS_ECDH_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_CAMELLIA_128_CBC_SHA
TLS_RSA_WITH_AES_256_CBC_SHA
TLS_RSA_WITH_CAMELLIA_256_CBC_SHA
TLS_RSA_WITH_SEED_CBC_SHA
SSL_RSA_FIPS_WITH_3DES_EDE_CBC_SHA
TLS_RSA_WITH_3DES_EDE_CBC_SHA
TLS_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_RC4_128_MD5
\end{verbatim}
\end{minipage}
\caption{Firefox 24}
\label{fig:ciphersuites:firefox}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\begin{minipage}[t][27ex][t]{0.30\textwidth}
\tiny
\begin{verbatim}
TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
TLS_DHE_RSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_ECDSA_WITH_CHACHA20_POLY1305_SHA256
TLS_ECDHE_RSA_WITH_CHACHA20_POLY1305_SHA256
TLS_RSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
TLS_DHE_RSA_WITH_AES_256_CBC_SHA
TLS_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_RC4_128_SHA
TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
TLS_DHE_RSA_WITH_AES_128_CBC_SHA
TLS_DHE_DSS_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_RC4_128_MD5
TLS_RSA_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_3DES_EDE_CBC_SHA
\end{verbatim}
\end{minipage}
\caption{Chrome 33}
\label{fig:ciphersuites:chrome}
\end{subfigure}

\caption{Differences in ciphersuites offered by
our \meekclient\ program when it accesses the network directly,
and by two web browsers.
The distinctive ciphersuites offered by \meekclient\ can be used as part of a blocking fingerprint.
As a remedy we have \meekclient\ proxy its TLS through a web browser extension.
}
\label{fig:ciphersuites}
\end{figure*}

@@

To explain the phenomenon, recall that we use browsers to handle HTTPS connections for meek in order
to hide TLS handshake characteristics.
Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
records meek's traffic.
In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
Google, click a result, and then close the tab that displays search results. The browser may close the 
connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
opens a new connection. In this case, small requests do not have such opportunity for batching.
